Local PCA results

### 2020-09-13 templated/summarize_run.Rmd

# original data files
chroms <- opt$bcf_file_names
bcf.files <- opt$bcf_files
names(bcf.files) <- chroms

@@

Now, we'll look at PCA plots from the extracted corners.
(this is done without a ton of memory by accumulating the covariance matrix in `running_cov`):
```{r corner_pca, cache=TRUE}
corner.npc <- 4
corner.regions <- vector(mode='list', length=ncol(mds.corners))
for (k in seq_along(corner.regions)) {
    corner.regions[[k]] <- regions[ mds.corners[,k],]
}
corner.covmats <- vector(mode='list', length=ncol(mds.corners))
for (k in seq_along(corner.covmats)) {
    reg <- regions[ mds.corners[,k], ]
    qfun <- multi_vcf_query_fn( chrom.list=chroms, file=bcf.files, regions=reg )
    corner.covmats[[k]] <- running_cov(qfun,1:nrow(reg), normalize.rows=TRUE)
}
corner.pca <- vector(mode='list', length=ncol(mds.corners))
for (k in seq_along(corner.pca)) {
    corner.pca[[k]] <- cov_pca(covmat=corner.covmats[[k]], k=corner.npc, w=opt$weights)
}
```

>>>>

# original data files
chroms <- opt$chrom_names
bcf.files <- opt$bcf_files
names(bcf.files) <- chroms

@@

Now, we'll look at PCA plots from the extracted corners.
(this is done without a ton of memory by accumulating the covariance matrix in `running_cov`):
```{r corner_pca, cache=TRUE, echo=-1}
options(datatable.fread.input.cmd.message=FALSE)
corner.npc <- 4
corner.regions <- vector(mode='list', length=ncol(mds.corners))
for (k in seq_along(corner.regions)) {
    corner.regions[[k]] <- regions[ mds.corners[,k],]
}
corner.covmats <- vector(mode='list', length=ncol(mds.corners))
for (k in seq_along(corner.covmats)) {
    reg <- regions[ mds.corners[,k], ]
    qfun <- multi_vcf_query_fn( chrom.list=chroms, file=bcf.files, regions=reg )
    corner.covmats[[k]] <- running_cov(qfun,1:nrow(reg), normalize.rows=TRUE)
}
corner.pca <- vector(mode='list', length=ncol(mds.corners))
for (k in seq_along(corner.pca)) {
    corner.pca[[k]] <- cov_pca(covmat=corner.covmats[[k]], k=corner.npc, w=opt$weights)
}
```
